Figure 7 - heterodimer

### 2024-08-06 ms_figure_7_heterodimer.Rmd
Reorder panels Fig7

## Create MA plots
rngY <- range(sapply(resList, function(rl) rl$log2FoldChange))
rngX <- range(sapply(resList, function(rl) log10(rl$baseMean)))
maplots <- lapply(structure(names(resList), names = names(resList)), function(nm) {
    ggplot(as.data.frame(resList[[nm]]), 
           aes(x = log10(baseMean), y = log2FoldChange)) + 
        geom_point(mapping = aes(color = abs(log2FoldChange) > 3 & 
                                     padj < 0.001), alpha = 0.25) + 
        scale_color_manual(values = c(`TRUE` = main_colors[4], `FALSE` = pt_color)) + 
        coord_cartesian(xlim = rngX, ylim = rngY) + 
        geom_text_repel(data = as.data.frame(resList[[nm]]) |>
                            tibble::rownames_to_column("gene") |>
                            dplyr::filter(gene == nm | 
                                              (log2FoldChange > 4.5 & padj < 0.05)), 
                        aes(label = gene), 
                        min.segment.length = 0, max.overlaps = Inf) + 
        theme_cowplot() + 
        labs(x = "Mean expression", y = "log2(fold-change)", 
             title = paste0(nm, "\U141E")) + 
        theme(legend.position = "none",
              plot.title = element_text(face = "italic"))
})

@@

fig7c <- wrap_plots(maplots, ncol = 2)

>>>>

## Create MA plots
rngY <- range(sapply(resList, function(rl) rl$log2FoldChange))
rngX <- range(sapply(resList, function(rl) log10(rl$baseMean)))
maplots <- lapply(structure(names(resList), names = names(resList)), function(nm) {
    ggplot(as.data.frame(resList[[nm]]), 
           aes(x = log10(baseMean), y = log2FoldChange)) + 
        geom_point(mapping = aes(color = abs(log2FoldChange) > 3 & 
                                     padj < 0.001, 
                                 alpha = abs(log2FoldChange) > 3 & 
                                     padj < 0.001)) + 
        scale_color_manual(values = c(`TRUE` = main_colors[4], `FALSE` = pt_color)) + 
        scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = 0.25)) + 
        coord_cartesian(xlim = rngX, ylim = rngY) + 
        geom_text_repel(data = as.data.frame(resList[[nm]]) |>
                            tibble::rownames_to_column("gene") |>
                            dplyr::filter(gene == nm | 
                                              (log2FoldChange > 4.5 & padj < 0.05)), 
                        aes(label = gene), 
                        min.segment.length = 0, max.overlaps = Inf) + 
        theme_cowplot() + 
        labs(x = "Mean expression", y = "log2(fold-change)", 
             title = paste0(nm, "\U141E")) + 
        theme(legend.position = "none",
              plot.title = element_text(face = "italic"))
})

@@

fig7c <- wrap_plots(maplots[c(2, 1)], ncol = 2)
